BOLD Parameter Estimation Using Particle Filters

### 2010-06-30 doc/thesis/background.tex
just a note added
conclusion in background

\chapter{Prior Works}
The ultimate purpose of this work is to provide a new tool
for analyzing FMRI data.

@@

\section{Conclusion}
In summary, several other approaches could be taken

>>>>

\chapter{Prior Works}
\label{sec:Prior Works}
The ultimate purpose of this work is to provide a new tool
for analyzing FMRI data.

@@

[might want to mention dynamic causal modeling]

\section{Conclusion}
Clearly there is no ideal solution to solving this system of nonlinear
equations. Exhaustive search type methods such as those employed by
\cite{Johnston2008} and \cite{Vakorin2007} can have extremely long
run times even for a single voxel. While Volterra models are an interesting
solution,there have not yet been exhaustive tests to determine whether
such approximations work well throughout state space. The most promising
method of those reviewed here is the Kalman filter based method. It is
able to maintain a very fast runtime while still approaching the solution.
While the reliance on a Gaussian estimate to the true posterior distribution could
cause problems, some modifications could make it extremely powerful. 
The particle filter method proposed in the next section bears a strong 
resemblance to the unscented Kalman filter; albeit with more point estimating
the posterior.

### 2010-06-30 doc/thesis/intro.tex
conclusion in background

\section{Noise}
As demonstrated in \autoref{sec:BOLD Phsyiology} the BOLD response has been
extensively studied and despite minor discrepancies, the cause of the BOLD 
signal is well known. However, as FMRI detects an  
aggregate signal over the space of cubic centimeters, there are
plenty of sources of noise. Though local neurons act
"together" (i.e. around the same time), the density of neurons, the
density of capillaries, and slight differences in activation across 
a particular voxel can all lead to signal attenuation and noise.

>>>>

\section{Noise}
\label{sec:Introduction Noise}
As demonstrated in \autoref{sec:BOLD Phsyiology} the BOLD response has been
extensively studied and despite minor discrepancies, the cause of the BOLD 
signal is well known. However, as FMRI detects an  
aggregate signal over the space of cubic centimeters, there are
plenty of sources of noise. Though local neurons act
"together" (i.e. around the same time), the density of neurons, the
density of capillaries, and slight differences in activation across 
a particular voxel can all lead to signal attenuation and noise.

### 2010-06-30 doc/thesis/particlefilters.tex
conclusion in background

\chapter{Particle Filters}
\label{sec:Particle Filter}
\section{Introduction}
Particle filters, a type of Sequential Monte Carlo (SMC) methods
are a powerful way of estimating the posterior probability distribution
of a set of parameters give a timeseries of measurements. Unlike Markov 
Chain Monte Carlo estimation, Sequential Monte-Carlo methods are designed
to be used with parameters that vary with time. Unlike variations of the
Kalman filter, particle filters do not make the assumption that noise
is Gaussian. Thus particle filters are often the best solution to bayesian 
tracking for non-linear, non-gaussian systems.

>>>>

\chapter{Particle Filters}
\label{sec:Particle Filter}
\section{Introduction}
Particle filters, a type of Sequential Monte Carlo (SMC) methods,
are a powerful way of estimating the posterior probability distribution
of a set of parameters give a timeseries of measurements. Unlike Markov 
Chain Monte Carlo estimation, Sequential Monte-Carlo methods are designed
to be used with parameters that vary with time. Unlike variations of the
Kalman filter, particle filters do not make the assumption that noise
is Gaussian. Thus particle filters are often the best solution to bayesian 
tracking for non-linear, non-gaussian systems.
